Visual narratives of the Covid-19 pandemic

### 2022-01-04 JDSSV_manuscript_knitr.Rnw
Some comments and sketches

\begin{document}
\SweaveOpts{concordance=TRUE}
<<include=FALSE, cache=FALSE, echo=FALSE, purl=FALSE>>=
library(knitr)
opts_chunk$set(comment = NA, size = 'footnotesize', prompt = TRUE, highlight = FALSE, 
               cache = TRUE, crop = TRUE, concordance = FALSE, fig.align='center',
               fig.path='Figures_R/fig-',out.width="0.4\\textwidth")
opts_knit$set(out.format = "latex")
knit_hooks$set(crop = hook_pdfcrop)
options(width = 80, prompt = "R> ", continue = "    ", digits = 3)
thm <- knit_theme$get('default')
Sys.setenv(TEXINPUTS=getwd(),
           BIBINPUTS=getwd(),
           BSTINPUTS=getwd())
knit_theme$set(thm)
@

@@

@@

\

\section[]{Comparisons and rankings}

@@

\section{Correspondence Analysis} \label{sec:models}

>>>>

\begin{document}
% \SweaveOpts{concordance=TRUE}
<<include=FALSE, cache=FALSE, echo=FALSE, purl=FALSE>>=
library(knitr)
opts_chunk$set(comment = NA, size = 'footnotesize', prompt = TRUE, highlight = FALSE, 
               cache = TRUE, crop = TRUE, concordance = FALSE, fig.align='center',
               fig.path='Figures_R/fig-',out.width="0.4\\textwidth")
opts_knit$set(out.format = "latex")
knit_hooks$set(crop = hook_pdfcrop)
options(width = 80, prompt = "R> ", continue = "    ", digits = 3)
thm <- knit_theme$get('default')
Sys.setenv(TEXINPUTS=getwd(),
           BIBINPUTS=getwd(),
           BSTINPUTS=getwd())
knit_theme$set(thm)
@

@@

% May also want to mention at the outset the limitations in the data due to low testing capacity, weekly effects due to reporting, and so on. We must be able to represent the data that exist visually while acknowledging the limitations associated with that data.

@@

\section{Time series}
% Line plots, frequency domain, NY times tile plots w/ cases represented in color intensity

\section[]{Comparisons and rankings}
% https://twitter.com/AndToddsaid/status/1314231055096971265 is a horrible set of graphs and a great example of the snark associated with covid management policy and geographic comparisons...

@@

% Discussion of how this section's conclusions change with the pandemic

% Focus primarily on time-series graphs (as opposed to log scales in color)

% Problems with log scales

% Problems with linear scales

% Discussion of sites which allow the user to switch back and forth between scales
